---
title: "WGL_DATA"
output: html_document
date: "`r Sys.Date()`"
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Clear Environment

```{r}
rm(list=ls())
```


# Setup
```{r}
library(tidyverse)
```

# Import Data

```{r}

  # Prepare list of data files
  txt_file_list = list.files(
    path = "data/",
    pattern = "*.TXT"
    )
  
  wgl_data <- tibble()
  wgl_data <- wgl_data[-1,]
  
  # Read in all files (this may take a moment)
  i = 0
  for (txt in txt_file_list) {
    # read the comma delimited file
    temp <- read_delim(
      paste0("data/", txt),
      delim = ",",
      ) %>% 
      # Make sure all columns are parsed as numeric
      mutate_if(is.character, parse_number) %>% 
    mutate(reading = row_number())                                # Add the reading number)
    temp <- temp %>% mutate(file = txt)                           # make a new column "file" to differentiate files
    wgl_data <- bind_rows(wgl_data, temp)                         # add the new data to the full dataset
    i <- i + 1
  }
  
  # Create a cache of the raw data
  saveRDS(wgl_data, file = "cache/wgl_data.RDS")
  rm(temp) # remove temp df to save space
```

# Clean the data

```{r}
# Rename columns to more intuitive names
wgl_data_clean <- wgl_data %>% 
  rename(
    cond.uS = `EC`,
    pressure.mbar = `PRESS`,
    depth.m = `DEPTH`,
    altitude.m = `ALT`,
    temp.C = `TEMP`
    ) %>% 
  mutate(
    file = str_replace(file, ".TXT", "")          # remove file extension from filename
  ) %>% 
  # Remove rows containing missing
  filter(
    across(
      .cols = everything(),
      .fns = ~ !is.na(.x)
    )
  )
```


# Plot

## raw

This plot shows all data for a specific file

```{r}
p_all <- wgl_data_clean %>%
  # for a specific file
  filter(file == "23JAN23_NSHQ14_300m") %>%
  filter(cond.uS < 1e4) %>% 
  pivot_longer(
    cols = c(cond.uS, depth.m, pressure.mbar, temp.C, altitude.m),
    names_to = "measurement",
    values_to = "value"
    ) %>% 
  ggplot(
    aes(
      x = reading,
      y = value,
      color = file
    )
  ) +
  geom_point() +
  facet_wrap(
    vars(measurement), 
    scales = "free", 
    nrow = 2,
    strip.position = "left"
    ) +
  scale_color_viridis_d() +
  labs(
    x = "reading",
    y = ""
  ) +
  theme_bw() +
  theme(
    legend.position = "bottom",
    strip.background = element_blank(),
    strip.placement = "outside"
  )

p_all
```

## NSHQ14 

Open fractures?

```{r}
wgl_data_clean %>% 
  filter(file == "23JAN23_NSHQ14_300m") %>%
  filter(cond.uS < 1e4) %>% 
  mutate(
    dir = case_when(
      reading > 2045 ~ "ascending", 
      reading <= 2045 ~ "descending")
    ) %>%
  ggplot(
    aes(
      y = depth.m,
      x = cond.uS,
      color = dir
    )
  ) +
  geom_point(alpha = 0.5) +
  scale_y_reverse(breaks = c(0, 50, 100, 150, 200, 250)) +
  scale_colour_viridis_d(begin = 0.2, end = 0.7) +
  labs(
    title = "WGL2023: NSHQ14",
    x = "Conductivity (µS/cm)",
    y = "Depth (m)"
  ) +
  theme_bw()
```

## BA4A 

The module hit an obstruction about 27 meters deep, we chose not to proceed out of caution.
```{r}
wgl_data_clean %>% 
  filter(file == "26JAN23_BA4A") %>%
  filter(cond.uS < 1e4) %>% 
  mutate(
    dir = case_when(
      reading > 729 ~ "ascending", 
      reading <= 729 ~ "descending")
    ) %>% 
  ggplot(
    aes(
      y = depth.m,
      x = depth.m,
      color = dir
    )
  ) +
  geom_path() +
  geom_point() +
  scale_y_reverse() +
  coord_cartesian(xlim = c(0, 30)) +
  labs(
    title = "WGL2023: BA4A",
    x = "Conductivity (µS/cm)",
    y = "Depth (m)"
  ) +
  theme_bw()
```

## BA1D 

We measured conductivity from a 250m sample to be ~550µS. We profiled this well in order to confirm whether our sample was representative of the deep fluids or if the bailer had a leak on the way up. Here it looks like the cond below 150m is > 1000; suggests a leak in the bailer.


```{r}
wgl_data_clean %>% 
  filter(file == "27JAN23_BA1D_300m") %>%
  mutate(
    dir = case_when(
      reading > 961 ~ "ascending", 
      reading <= 961 ~ "descending")
    ) %>% 
  filter(cond.uS < 3000) %>% 
  ggplot(
    aes(
      y = depth.m,
      x = cond.uS,
      color = dir
    )
  ) +
  geom_path() +
  geom_point() +
  scale_y_reverse() +
  coord_cartesian(xlim = c(0, 3000)) +
  scale_colour_viridis_d(begin = 0.2, end = 0.7) +
  labs(
    title = "WGL2023: BA1D",
    x = "Conductivity (µS/cm)",
    y = "Depth (m)"
  ) +
  theme_bw()
```
